---
title: "SPY Prediction based on ARIMA Model"
author: "ETF Researcher"
date: "March 14, 2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read / Download SPY Data
```{r message=FALSE, warning=FALSE}
library(quantmod)
library(astsa)
library(fpp2)
```
```{r message=FALSE, warning=FALSE}
getSymbols("SPY", from = '2020-12-01', src = "yahoo")
stock <- SPY$SPY.Close

```
## Plot the stocks
```{r}
plot(stock)
```

## EDA

* ACF and PACF
```{r}
acf2(stock)
```

* Detrend
```{r}
plot(diff(stock))
```

* Rate of returns
```{r}
plot(diff(log(stock)))
```

* ACF and PACF after first order difference
```{r}
acf2(diff(stock))
```


## Model Building

* AR(1)
```{r, fig.height=6}
sarima(stock, 1, 0, 0)
```

* Plots overlays
```{r}
arimaAR1 <- arima(stock, order = c(1, 0, 0))

autoplot(ts(SPY$SPY.Close)) +
  autolayer(fitted(arimaAR1), series="Fitted") +
  ylab("$") + xlab("Time")
```

* ARIMA(1, 1, 0)
```{r}
sarima(stock, 1, 1, 0)
```

## Forecasting
```{r}
sarima.for(stock, 5, 1, 0, 0)
```

```{r}
sarima.for(stock, 5, 1, 1, 0)
```

## Use 'Forecast' or 'fpp2' package

* Auto Selection
```{r}
auto.arima(stock)
```
```{r}
arimaDiff1 <- arima(stock, order = c(0, 1, 0))

autoplot(ts(SPY$SPY.Close)) +
  autolayer(fitted(arimaDiff1), series="Fitted") +
  ylab("$") + xlab("Time")
```


* Explore more forecasting models
```{r}
forecast(auto.arima(stock), h=5) %>% autoplot()
```
```{r}
forecast(Arima(stock, order = c(1, 0, 0)), h=5) %>% autoplot()
```
```{r}
forecast(Arima(stock, order = c(1, 1, 1)), h=5) %>% autoplot()
```

* Check Residuals
```{r}
checkresiduals(Arima(stock, order = c(1, 1, 1)))
```
```{r}
checkresiduals(Arima(stock, order = c(1, 1, 0)))
```

```{r}
checkresiduals(Arima(stock, order = c(1, 0, 0)))
```
```{r}
checkresiduals(Arima(stock, order = c(0, 1, 0)))
```

## Cross Validation on Different Models
```{r}
fArima <- function(x, h) {
  forecast(auto.arima(x), h=h)
}

errorArima <- tsCV(stock, fArima, window = 20, h = 5)

mean(errorArima^2, na.rm = TRUE)
```

## Naive Model
```{r}
fNaive <- function(x, h) {
  forecast(naive(x, h), h = h)
}

errorNaive <- tsCV(stock, fNaive, window = 20, h = 5)
mean(errorNaive^2, na.rm = TRUE)
```

## ETS Model
```{r}
fETS <- function(x, h) {
  forecast(ets(x), h = h)
}

errorETS <- tsCV(stock, fETS, window = 20, h = 5)
mean(errorETS^2, na.rm = TRUE)
```

## Models for Selection

* Simplicity
* Avoid over-fitting
* Speed

```{r}
forecast(Arima(stock, order = c(1, 0, 0)), h=5) %>% autoplot()
```
```{r}
forecast(ets(stock), h = 5) %>% autoplot()
```
```{r}
etsModel <- ets(stock)

autoplot(ts(SPY$SPY.Close)) +
  autolayer(fitted(etsModel), series="Fitted") +
  ylab("$") + xlab("Time")
```

```{r}
forecast(naive(stock, 5), h = 5) %>% autoplot()
```

```{r}
naiveModel <- naive(stock, 5)

autoplot(ts(SPY$SPY.Close)) +
  autolayer(fitted(naiveModel), series="Fitted") +
  ylab("$") + xlab("Time")
```
