---
title: "China Stocks Report"
author: "ETF Researcher"
date: "March 31, 2021"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Read Data for China Stocks
Reference from :
https://www.investors.com/news/best-chinese-stocks-to-buy/?src=A00220

```{r message=FALSE, warning=FALSE}
library(readr)
library(quantmod)
library(PerformanceAnalytics)
```

## Selected stocks in different sectors
```{r}
stocksGeneral <- c("BABA", "JD", "PDD", "TCEHY", "VIPS",
                   "BIDU", "TME", "NTES", "TCOM", "DADA", 
                   "YY", "BEKE", "BILI")

stocksEV <- c("NIO", "XPEV", "LI", "BYDDF")

stocksFin <- c("FUTU", "TIGR", "QFIN")

stocksSolar <- c("DQ", "JKS")

# stocksEdu <- c("EDU", "TAL", "YQ", "GSX")
stocksEdu <- c("EDU", "TAL", "YQ") # symbol GSX removed

stocksOther <- c("YSG", "GDS")

```

## Get Stocks Data from Yahoo Finance

* Define a function to obtain data and candleChart

```{r}
get_data <- function(ETFsymbols, start_date, selectedStd, selectedRtn){
  
  # store data in a new environment
  stocksEnv <- new.env()
  getSymbols(ETFsymbols, env = stocksEnv, 
           from = start_date, src = "yahoo")
  

  # produce return report
  goodCandidate <- data.frame()

  for (stock in ETFsymbols) {
    dret <- dailyReturn(stocksEnv[[stock]])
    pret <- Return.cumulative(dret)
    if (sd(dret) < selectedStd && as.numeric(pret) > selectedRtn) {
      tmp <- data.frame(Symbol = stock, 
                        sd = round(sd(dret), 3), 
                        ret = round(as.numeric(pret), 3))
      goodCandidate <- rbind(goodCandidate, tmp)
      
    }
  }
  
  # check the list
  # goodCandidate
  
  # produce candleChart for selected stocks
  for (stock in goodCandidate$Symbol) {
  candleChart(stocksEnv[[stock]], name = stock)
  }
  
  goodCandidate
  
}
```

## General Stocks

```{r message=FALSE, warning=FALSE}
return_report <- get_data(stocksGeneral, '2022-01-01', 0.10, -0.5)
```

### Return Table for Stocks

```{r}
return_report
```
## EV Stocks
```{r}
return_report <- get_data(stocksEV, '2022-01-01', 0.10, -0.5)
```

### Return Table for EV Stocks
```{r}
return_report
```

## Financial Stocks
```{r}
return_report <- get_data(stocksFin, '2022-01-01', 0.10, -0.5)
```

## Return for Financial Stocks
```{r}
return_report
```

## Solar Stocks

```{r}
return_report <- get_data(stocksSolar, '2022-01-01', 0.10, -0.5)
```

## Return for Solar Stocks
```{r}
return_report
```

## Education Stocks

```{r}
return_report <- get_data(stocksEdu, '2022-01-01', 0.50, -1.5)
```

## Return for Education Stocks
```{r}
return_report
```

## Multi Areas Stocks

```{r}
return_report <- get_data(stocksOther, '2022-01-01', 0.10, -0.5)
```

## Return for Multi-Area Stocks
```{r}
return_report
```

