---
title: "ETF Screening Report"
author: "ETF Reseacher"
date: "December 25, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Preparation
```{r message=FALSE, warning=FALSE}
# https://etfdb.com/compare/market-cap/

library(readr)
library(quantmod)
library(PerformanceAnalytics)
library(dplyr)
```
### Import ETF List
```{r message=FALSE, warning=FALSE}
companylist <- read_csv("etfdb_full_list.csv") # prepared in excel
colnames(companylist) <- c("Symbol", "ETF_name", "Asset_class", 
                           "Total_assets", "YTD_Price_Change", 
                           "Daily_Volume", "Close_price", "Pro")
head(companylist)
```
### Clean Up the Table

* What types of ETFs
```{r}
companylist["Pro"] <- NULL
companylist$Total_assets <- as.numeric(gsub('[$,]', '', 
                                            companylist$Total_assets))
companylist$Asset_class <- as.factor(companylist$Asset_class)

table(companylist$Asset_class)
```
### Select ETFs with Total Assets >= $100 Million

* How many ETFs have total assets higher than 100 million USD
```{r}
companylist <- companylist %>% 
  filter(Total_assets >= 100 & Asset_class == "Equity")
nrow(companylist)
```
## AI ETFs
```{r}
stockSymbols <- companylist["Symbol"]
idx_ai <- grepl('Artificial', companylist$ETF_name) 
sampledStocks <- stockSymbols[idx_ai, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx_ai, ]
companylist_idx[, 1:2]
```

```{r}
for (stock in sampledStocks$Symbol) {
  candleChart(stocksEnv[[stock]], name = stock)
}
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

## Cyber Security ETFs
```{r}
idx_cyber <- grepl('Cyber', companylist$ETF_name)
sampledStocks <- stockSymbols[idx_cyber, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```

```{r}
companylist_idx <- companylist[idx_cyber, ]
companylist_idx[, 1:2]
```
```{r}
for (stock in sampledStocks$Symbol) {
  candleChart(stocksEnv[[stock]], name = stock)
}
```

### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

## Clean Energy ETFs
```{r message=FALSE, warning=FALSE}
idx_clean <- grepl('Clean', companylist$ETF_name) | 
  grepl('Solar', companylist$ETF_name) | 
  grepl('Battery', companylist$ETF_name)
sampledStocks <- stockSymbols[idx_clean, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx_clean, ]
companylist_idx[, 1:2]
```

```{r}
for (stock in sampledStocks$Symbol) {
  candleChart(stocksEnv[[stock]], name = stock)
}
```

### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```
