---
title: "ETF Screening Report"
author: "ETF Researcher"
date: "May 1, 2021"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Preparation
```{r message=FALSE, warning=FALSE}
# https://etfdb.com/compare/market-cap/

library(readr)
library(quantmod)
library(PerformanceAnalytics)
library(dplyr)
```
### Import ETF List
```{r message=FALSE, warning=FALSE}
companylist <- read_csv("selectedStocksETFs.csv") # prepared in excel
colnames(companylist) <- c("Symbol", "ETF_name", "Asset_class", 
                           "Total_assets", "YTD_Price_Change", 
                           "Daily_Volume", "Close_price", "Day_Change",
                           "Label")
head(companylist)
```
### Clean Up the Table

* What types of ETFs according to sectors / industries
```{r}
# companylist["Pro"] <- NULL
# companylist$Total_assets <- as.numeric(gsub('[$,]', '', 
#                                             companylist$Total_assets))
# companylist$Asset_class <- as.factor(companylist$Asset_class)

table(companylist$Asset_class)
```
### Select ETFs with Total Assets >= $50 Million

* How many ETFs have total assets higher than 20 million USD
```{r}
# companylist <- companylist %>% 
#   filter(Total_assets >= 20 & Daily_Volume >= 5000)
nrow(companylist)
```
```{r}
# start date to select
start_date <- "2021-01-01"

selectedStd <- 0.05 # daily
selectedRtn <- 0    # accumulative
```

## Get ETFS Data from Yahoo Finance

* Define a function to obtain data and candleChart
```{r}
get_data <- function(sector, start_date, selectedStd, selectedRtn){
  sampledStocks <- subset(companylist, Label == sector)
  
  # store data in a new environment
  stocksEnv <- new.env()
  getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = start_date, src = "yahoo")
  

  # produce return report
  goodCandidate <- data.frame()

  for (stock in sampledStocks$Symbol) {
    dret <- dailyReturn(stocksEnv[[stock]])
    pret <- Return.cumulative(dret)
    if (sd(dret) < selectedStd && as.numeric(pret) > selectedRtn) {
      tmp <- data.frame(Symbol = stock, 
                        sd = round(sd(dret), 3), 
                        ret = round(as.numeric(pret), 3))
      goodCandidate <- rbind(goodCandidate, tmp)
      
    }
  }
  
  # check the list
  # goodCandidate
  
  # produce candleChart for selected stocks
  for (stock in goodCandidate$Symbol) {
  candleChart(stocksEnv[[stock]], name = stock)
  }
  
  goodCandidate
  
}
```


## Artificial Intelligence (AI) ETFs

```{r message=FALSE, warning=FALSE}
return_report <- get_data('AI', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```

## Software and Cyber Security

```{r}
return_report <- get_data('Software', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```

## Semiconductor

```{r}
return_report <- get_data('Semiconductor', '2021-01-01', 0.05, 0.00)
```


```{r}
return_report
```

## Oil and Gas (OilGas)
```{r}
return_report <- get_data('OilGas', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```

## Natural Resources (NaturalResource)

```{r}
return_report <- get_data('NaturalResource', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```

## MLP (MLP)

```{r}
return_report <- get_data('MLP', '2021-01-01', 0.05, 0.00)
```
```{r}
return_report
```

## Medical Device (MedicalDevice)

```{r}
return_report <- get_data('MedicalDevice', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```


## Media (Media)

```{r}
return_report <- get_data('Media', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```

## Battery

```{r}
return_report <- get_data('Battery', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Internet

```{r}
return_report <- get_data('Internet', '2021-01-01', 0.05, 0.00)
```

```{r}
return_report
```
## Internet Security (InternetSecurity)

```{r}
return_report <- get_data('InternetSecurity', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report 
```

## Infrastructure

```{r}
return_report <- get_data('Infrastructure', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```
## Home

```{r}
return_report <- get_data('Home', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Health Care

```{r}
return_report <- get_data('Healthcare', '2021-01-01', 0.05, -0.5)
```
```{r}
return_report
```

## Gold Mining (GoldMine)

```{r}
return_report <- get_data('GoldMine', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```
## Finanical Service (FinService)

```{r}
return_report <- get_data('FinService', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Consumer

```{r}
return_report <- get_data('Consumer', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Clean Energy (CleanEnergy)

```{r}
return_report <- get_data('CleanEnergy', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```
## Utilities

```{r}
return_report <- get_data('Utilities', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Telecom

```{r}
return_report <- get_data('Telecom', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Technology

```{r}
return_report <- get_data('Technology', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Real Estate

```{r}
return_report <- get_data('RealEstate', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Materials

```{r}
return_report <- get_data('Materials', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```


## Industrials

```{r}
return_report <- get_data('Industrials', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Healthcare General(HealthcareG)

```{r}
return_report <- get_data('HealthcareG', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Financials

```{r}
return_report <- get_data('Financials', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Staples

```{r}
return_report <- get_data('Staples', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Consumer Discretionary (ConsumerD)

```{r}
return_report <- get_data('ConsumerD', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Biotechnology

```{r}
return_report <- get_data('Biotechnology', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Banks

```{r}
return_report <- get_data('Banks', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report 
```


## Airlines

```{r}
return_report <- get_data('Airlines', '2021-01-01', 0.05, -0.5)
```


## Aerospace and Defence (Aerospace)

```{r}
return_report <- get_data('Aerospace', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```


## Solar

```{r}
return_report <- get_data('Solar', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Silver

```{r}
return_report <- get_data('Silver', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Retail

```{r}
return_report <- get_data('Retail', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Transportation

```{r}
return_report <- get_data('Transportation', '2021-01-01', 0.05, -0.5)
```
```{r}
return_report
```


## Water

```{r}
return_report <- get_data('Water', '2021-01-01', 0.05, -0.5)
```
```{r}
return_report
```


## Game

```{r}
return_report <- get_data('Game', '2021-01-01', 0.05, -0.5)
```
```{r}
return_report
```

## Countries or Regions

```{r}
return_report <- get_data('Countries', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```
## Blockchain

```{r}
return_report <- get_data('Blockchain', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Cannabis

```{r}
return_report <- get_data('Cannabis', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## ARK

```{r}
return_report <- get_data('ARK', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

## Waste

```{r}
return_report <- get_data('Waste', '2021-01-01', 0.05, -0.5)
```

```{r}
return_report
```

