---
title: "ETF Screening Report"
author: "ETF Researcher"
date: "December 25, 2020"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Preparation
```{r message=FALSE, warning=FALSE}
# https://etfdb.com/compare/market-cap/

library(readr)
library(quantmod)
library(PerformanceAnalytics)
library(dplyr)
```
### Import ETF List
```{r message=FALSE, warning=FALSE}
companylist <- read_csv("simuStocksETFs.csv") # prepared in excel
colnames(companylist) <- c("Symbol", "ETF_name", "Asset_class", 
                           "Total_assets", "YTD_Price_Change", 
                           "Daily_Volume", "Close_price", "Day_Change",
                           "Label")
head(companylist)
```
### Clean Up the Table

* What types of ETFs according to sectors / industries
```{r}
# companylist["Pro"] <- NULL
# companylist$Total_assets <- as.numeric(gsub('[$,]', '', 
#                                             companylist$Total_assets))
# companylist$Asset_class <- as.factor(companylist$Asset_class)

table(companylist$Asset_class)
```
### Select ETFs with Total Assets >= $100 Million

* How many ETFs have total assets higher than 100 million USD
```{r}
companylist <- companylist %>% 
  filter(Total_assets >= 1000)
nrow(companylist)
```


## Artificial Intelligence (AI) ETFs
```{r message=FALSE, warning=FALSE}
stockSymbols <- companylist["Symbol"]
idx_ai <- companylist$Label == "AI"
sampledStocks <- stockSymbols[idx_ai, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx_ai, ]
companylist_idx[, 1:2]
```

### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```
```{r}
# store the sampled ETFs
ETFs_list_all <- data.frame()
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```


## Software and Cyber Security
```{r}
idx_software <- companylist$Label == "Software"
sampledStocks <- stockSymbols[idx_software, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```

```{r}
companylist_idx <- companylist[idx_software, ]
companylist_idx[, 1:2]
```

### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```
```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```

## Semiconductor
```{r}
idx_semi <- companylist$Label == "Semiconductor"
sampledStocks <- stockSymbols[idx_semi, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx_semi, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```

## Oil and Gas
```{r}
idx <- companylist$Label == "OilGas"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```

## Natural Resources
```{r}
idx <- companylist$Label == "NaturalResource"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## MLP
```{r}
idx <- companylist$Label == "MLP"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```

## Medical Device
```{r}
idx <- companylist$Label == "MedicalDevice"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```

## Media
```{r}
idx <- companylist$Label == "Media"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Battery
```{r}
idx <- companylist$Label == "Battery"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Internet
```{r}
idx <- companylist$Label == "Internet"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Internet Security
```{r}
idx <- companylist$Label == "InternetSecurity"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Infrastructure
```{r}
idx <- companylist$Label == "Infrastructure"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Home
```{r}
idx <- companylist$Label == "Home"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Health Care
```{r}
idx <- companylist$Label == "Healthcare"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Gold Mining
```{r}
idx <- companylist$Label == "GoldMine"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Finanical Service
```{r}
idx <- companylist$Label == "FinService"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Consumer
```{r}
idx <- companylist$Label == "Consumer"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Clean Energy
```{r}
idx <- companylist$Label == "CleanEnergy"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Utilities
```{r}
idx <- companylist$Label == "Utilities"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Telecom
```{r}
idx <- companylist$Label == "Telecom"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Technology
```{r}
idx <- companylist$Label == "Technology"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Real Estate
```{r}
idx <- companylist$Label == "RealEstate"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Materials
```{r}
idx <- companylist$Label == "Materials"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Industrials
```{r}
idx <- companylist$Label == "Industrials"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Healthcare General
```{r}
idx <- companylist$Label == "HealthcareG"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Financials
```{r}
idx <- companylist$Label == "Financials"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Staples
```{r}
idx <- companylist$Label == "Staples"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Consumer Discretionary
```{r}
idx <- companylist$Label == "ConsumerD"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Biotechnology
```{r}
idx <- companylist$Label == "Biotechnology"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Banks
```{r}
idx <- companylist$Label == "Banks"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Airlines
```{r}
idx <- companylist$Label == "Airlines"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Aerospace and Defence
```{r}
idx <- companylist$Label == "Aerospace"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Solar
```{r}
idx <- companylist$Label == "Solar"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Silver
```{r}
idx <- companylist$Label == "Silver"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Retail
```{r}
idx <- companylist$Label == "Retail"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Transportation
```{r}
idx <- companylist$Label == "Transportation"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Water
```{r}
idx <- companylist$Label == "Water"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```
## Game
```{r}
idx <- companylist$Label == "Game"
sampledStocks <- stockSymbols[idx, "Symbol"]
stocksEnv <- new.env()
getSymbols(sampledStocks$Symbol, env = stocksEnv, 
           from = "2020-01-01", src = "yahoo")
```
```{r}
companylist_idx <- companylist[idx, ]
companylist_idx[, 1:2]
```
### Check Returns and Standard Deviations

* Daily sd is less than 0.05
* Accumulative return > 8%
```{r}
goodCandidate <- data.frame()

for (stock in sampledStocks$Symbol) {
  dret <- dailyReturn(stocksEnv[[stock]])
  pret <- Return.cumulative(dret)
  if (sd(dret) < 0.05 && as.numeric(pret) > 0.08) {
    tmp <- data.frame(Symbol = stock, 
                      sd = round(sd(dret), 3), 
                      ret = round(as.numeric(pret), 3))
    goodCandidate <- rbind(goodCandidate, tmp)
    
  }
}

# check the list
goodCandidate

```

```{r}
ETFs_list_all <- rbind(ETFs_list_all, sampledStocks)
```

## Appendix: Candle Charts for Sampled ETFs
```{r echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
stocksEnv <- new.env()
getSymbols(ETFs_list_all$Symbol, env = stocksEnv, 
           from = "2020-07-01", src = "yahoo")

for (stock in ETFs_list_all$Symbol) {
  candleChart(stocksEnv[[stock]], name = stock)
}

# candleChart(ZM, subset = "2020")
# addSMA(n = 10, col = "white")
# addSMA(n = 50, col = "blue")
# addSMA(n = 200, col = "red")
# addRSI(n = 14, maType = "EMA")
# addBBands(n = 20, sd = 2)
# addMACD(fast = 12, slow = 26, signal = 9, type = "EMA")
# zoomChart(ZM, subset = "2020-06")
```

